CdGF_aucrf

### 2016-10-04 code/CdGF_AUCRF.Rmd
reduce features to decrease cage/inocula predictability

#random forest regression model to determine Day 0 OTU correlated with increased CFU
seed <- 1
n_trees <- 2001
iters <- 100
n_features <- 30
```

@@

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
euth_otus <- rf_early_aucrf$Xopt

aucrf_data <- Predict_early_euth_df[,c('Euth_Early',euth_otus)]

@@

#### leave-one-cage-out
LOcO_df <- Predict_df %>% 
                select(Euth_Early, cage_id, one_of(euth_otus))
cage_list <- as.character(unique(LOcO_df$cage_id))

@@

```{r importance, fig.width=10, fig.height=10}

#Importance Plot
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

@@

```{r partial dependence, fig.width=10, fig.height=10}
layout(matrix(c(1:20), nrow=5, byrow=TRUE))

>>>>

#random forest regression model to determine Day 0 OTU correlated with increased CFU
seed <- 1
n_trees <- 2001
iters <- 100
n_features <- 65
```

@@

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
euth_otu_feat <- rf_early_aucrf$Xopt

aucrf_data <- Predict_early_euth_df[,c('Euth_Early',euth_otu_feat)]

@@

#### leave-one-cage-out
LOcO_df <- Predict_df %>% 
                select(Euth_Early, cage_id, one_of(euth_otu_feat))
cage_list <- as.character(unique(LOcO_df$cage_id))

@@

```{r importance, fig.width=10, fig.height=5}

#Importance Plot
n_rf_features <- 5
euth_otus <- euth_otu_feat[1:n_rf_features]
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

@@

```{r partial dependence, fig.width=10, fig.height=5}
layout(matrix(c(1:6), nrow=2, byrow=TRUE))
